Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-09-21 presentation.tex
initial changes to presentation for PARCC conferencce

\documentclass{beamer} 
%\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

\begin{document}
\title[Unrecognized States: A Theory of Self-Determination and Foreign Influence\hspace{1.25in}\insertframenumber/\inserttotalframenumber]{Unrecognized States: A Theory of Self-Determination and Foreign Influence}
\author[Kristy Buzard, Benjamin Graham and Ben Horne]{Kristy Buzard, Benjamin Graham and Ben Horne\\ kbuzard@syr.edu}
\date{April 12, 2015}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\pause
In each period: secessionists and gov't each choose (simultaneously) among $\left\{\text{Fight, Status Quo, Cede}\right\}$
\pause
		\begin{itemize}
			\item We need SQ to be a stage game best response for both secessionists and gov't
		\end{itemize}

\pause
\vskip.2in
We add some more realistic elements:
\pause
		\begin{enumerate}[<+->]
			\item Unrecognized status reduces SQ payoffs of secessionists each period
			\item Patron and int'l community can make investments in both actors' payoffs
		\end{enumerate}

>>>>

%\documentclass{beamer} 
\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

\begin{document}
\title[Unrecognized States: A Theory of Self-Determination and Foreign Influence\hspace{1.25in}\insertframenumber/\inserttotalframenumber]{Unrecognized States: A Theory of Self-Determination and Foreign Influence}
\author[Kristy Buzard, Benjamin Graham and Ben Horne]{Kristy Buzard, Benjamin Graham and Ben Horne\\ kbuzard@syr.edu}
\date{September 23, 2016}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\pause
In each period: secessionists and gov't each choose (simultaneously) among $\left\{\text{Fight, Status Quo, Cede}\right\}$
\pause
		\begin{itemize}
			\item We need Status Quo to be a stage game best response for both secessionists and gov't
		\end{itemize}

\pause
\vskip.2in
We add some more realistic elements:
\pause
		\begin{enumerate}[<+->]
			\item Unrecognized status reduces Status Quo payoffs of secessionists each period
			\item Patron and int'l community can make investments in both actors' payoffs
		\end{enumerate}
